### 2022-08-07 paper/Chapters/Chapter01.tex
update paper

%% main problem, introduce deep learning, UNet
In 3D computer vision tasks, the \textit{point cloud} ( i.e. a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface. Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, which can be further used for  surface reconstruction, shadings generation and other visual effects. A common approach to acquire the surface normal from point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal. However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map. But due to the  optical noises and the reflections in dark and shinny areas of the object surface, the depth map is usually semi-dense only. Thus it limited the neighbor based approach since the missing data leads to less neighbors of each points. However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance. For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images. \cite{nconv} uses normalized convolution network to enhance semi-dense depth map to fully dense depth map. Either work takes in-complete input data and mends it to fully dense output. Thus a deep learning based approach can be a way to deal with the semi-dense depth map input for surface normal estimation task.

@@

%% introduce photometric stereo
Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations. The relative methods are typically solve the least square problem based on the pointwise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF). While BRDF based model generally cannot account the global illumination effects and this is usually unavoidable problem due to the light interactions and difficult traced mathematically.

@@

%% introduce the network, trip-net, dataset
One of our challenge is to apply the semi-dense input data to the neural network in a image-wise way. UNet is a good network applying for computer vision task with up-sampling requirement. We modified it with gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data. Another challenge is to merge the different input data feature maps together to cooperatively improved surface normal inference task. We propose a $ multi-fusion $ scheme for integration on separate feature map extractors. We will show that this multi-fusion design can be taken advantages of combination of different input data types and improved surface normal inference performance. To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios. To simulate depth maps in real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.

%% experiments
We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics. We compare our approach against the geometry information based approach based on the similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy. We also applied our model on real dataset and compare with the optimization based approach.

The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work. Chapter 2 briefly discusses the related work about normal inference. Chapter 3 is the main approaches of this work. Chapter 4 introduces the created dataset for the training work. Chapter 5 is the description of the experiments and the evaluation of the models. Chapter 6 is the conclusion of the whole thesis.

>>>>

%% main problem, introduce deep learning, UNet
In 3D computer vision tasks, the \textit{point cloud} ( i.e. a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface. Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, and it can be further used for surface reconstruction, shadings generation and other visual effects. A common approach to acquire the surface normal from the point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal. However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map. But due to the optical noises and the reflections in dark and shiny areas of the object surface, the depth map is usually semi-dense only. Thus it limited the neighbor based approach since the missing data leads to fewer neighbors of each point. However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance. For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images. \cite{nconv} uses normalized convolution network to enhance the semi-dense depth map to fully dense depth map. Either work takes in-complete input data and mends it to fully dense output. Thus a deep learning based approach can be a way to deal with the semi-dense depth map input for surface normal estimation task.

@@

%% introduce photometric stereo
Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations. The relative methods are typically solve the least square problem based on the point-wise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF). While BRDF based model generally cannot account the global illumination effects and this is usually an unavoidable problem due to the light interactions and difficult traced mathematically.

@@

%% introduce the network, trip-net, dataset
One of our challenges is to apply the semi-dense input data to the neural network in an image-wise way. UNet is a good network applying for computer vision tasks with up-sampling requirements. We modified it with a gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data. Another challenge is to merge the different input data feature maps to cooperatively improved the surface normal inference task. We propose a $ multi-fusion $ scheme for integration on separate feature map extractors. We will show that this multi-fusion design can be taken advantage of by a combination of different input data types and improved surface normal inference performance. To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios. To simulate depth maps in the real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.

%% experiments
We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics. We compare our approach against the geometry information based approach based on similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy. We also applied our model to a real dataset and compare it with the optimization based approach.

The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work. Chapter 2 briefly discusses the related work about normal inference. Chapter 3 is the main approach of this work. Chapter 4 introduces the created dataset for the training work. Chapter 5 is the description of the experiments and the evaluation of the models. Chapter 6 is the conclusion of the whole thesis.
